%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

\usepackage[utf8]{inputenc} % UTF8 encoding

%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------

\profilepic{} % Profile picture

\cvname{Bruno BELANYI} % Your name
\cvjobtitle{Computer Science Student} % Job title/career

\cvdate{04 November 1999} % Date of birth
\cvaddress{Kremlin-Bicêtre, France} % Current address
\cvmail{bruno.belanyi@gmail.com} % Mail address
\cvnumberphone{+33 7 81 59 44 86} % Phone number
\cvsite{linkedin.com/in/bruno-belanyi} % Personal website

%-------------------------------------------------------------------------------

\begin{document}

%-------------------------------------------------------------------------------
% ABOUT ME
%-------------------------------------------------------------------------------

\aboutme{
  Currently a fourth year student at EPITA, I am looking for an end-of-studies
  internship abroad.
}

%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{
  {Algorithms \& Data Stuctures/5},
  {Docker/3},
  {Git/5.5},
  {Bash/4},
  {Caml/2},
  {SQL/4.5},
  {Java/4},
  {Python/5},
  {C/4.6},
  {Rust/4.6},
  {C++/5}}

\skillstext{
  {Independent / 5 \newline},
  {Team work / 5 \newline},
  {Microsoft Office / 4 \newline},
  {Linux \& UNIX / 4.5 \newline}} % Same thing, without the progress bar

\makeprofile % Print the sidebar

%-------------------------------------------------------------------------------
% INTERESTS
%-------------------------------------------------------------------------------

\section{Interests}

I am interested in computer science and engineering in a broad sense. Always
checking out new technologies and programming languages that pique my interest.
I am also fond of mathematics, physics, and science in a broader sense.

I am majoring in Image Processing, however I am interested in all topics
relating to high-performance computing and optimisation.

%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------

\section{Education}

\begin{twenty} % Environment for a list with descriptions
  %\twentyitem{<dates>}{<title>}{<location>}{<description>}
  %\twentyitemshort{<dates>}{<title/description>}

  \twentyitem{2018-Now}
    {Computer Science}
    {EPITA, Kremlin-Bicêtre, France}
    {Majoring in Image Processing.}

  \twentyitem{2016-2018}
    {Preparatory School}
    {CPGE Corneille, Rouen, France}
    {MPSI \& MP$\star$ --- Maths and Physics Engineering Preparatory Classes,
    specialized in Computer Science.}

  \twentyitem{2013-2016}
    {High School}
    {Institution Jean-Paul II, Rouen, France}
    {Bacalauréat S with honors.}

\end{twenty}

%-------------------------------------------------------------------------------
% EXPERIENCE
%-------------------------------------------------------------------------------

\section{Experience}

\begin{twenty}

  \twentyitem{Jul'20-Jan'21}
    {Teaching Assistant (ACU)}
    {EPITA, Kremlin-Bicêtre, France}
    {Tutoring 3rd year students in C, UNIX, \& software development through
    workshops, oral presentations, and programming projects.}

  \twentyitem{Jan-Jul'20}
    {Teaching Assistant (YAKA)}
    {EPITA, Kremlin-Bicêtre, France}
    {Tutoring 3rd year students in C++, Java, \& SQL through oral presentations
    and programming projects.}

  \twentyitem{Sep-Dec'19}
    {Natural Language Processing}
    {Algolia, Paris, France}
    {Building a Semantic Decompounding Library for Python \& C++}

\end{twenty}

%-------------------------------------------------------------------------------
% PROJECTS
%-------------------------------------------------------------------------------


\section{School Projects}

\begin{twenty}

  \twentyitem{2nd Year Ing.}
    {Pathtracer}
    {Rust - 1 month}
    {A physically based renderer of scenes described in a custom YAML format.}

  \twentyitem{1st Year Ing.}
    {Tiger Compiler}
    {C++ - 3 months}
    {A full featured compiler in modern C++, following Andrew Appel's
    \textit{Modern Compiler Implementation in ML}}

  \twentyitem{1st Year Ing.}
    {Bistromathique}
    {C++ - 36 hour rush}
    {A templated big-integer library and calculator, completed individually.}

\end{twenty}

%-------------------------------------------------------------------------------
% OTHER INFORMATION
%-------------------------------------------------------------------------------


\section{Other Information}

\subsection{Hobbies}

\begin{twenty}

  \twentyitemshort{}
    {Archery}

  \twentyitemshort{}
    {Self-hosting various services on a VPS using Docker}

\end{twenty}

\subsection{Achievements \& Extra-curriculars}

\begin{twenty}

  \twentyitem{Jan-Jul'20}
    {Chief Tiger Maintainer}
    {EPITA}
    {A small team of assistants is chosen each year to improve the project, keep
    it up-to-date, as well as presenting each stage of the project to the
    students and guide them along the way.}

  \twentyitem{2012}
    {Maths Olympiads (School Level)}
    {Rouen, France}
    {First place at the \textit{René Merckhoffer} contest of Normandy.

    This lead to a couple of two-weeks formation with \textit{Animath} on
    Olympic-maths.}

\end{twenty}

%-------------------------------------------------------------------------------
% SECOND PAGE EXAMPLE
%-------------------------------------------------------------------------------

%\newpage % Start a new page

%\makeprofile % Print the sidebar

%\section{Other information}

%\subsection{Review}

% Lorem ipsum.

%\section{Other information}

%\subsection{Review}

% Lorem ipsum.

%-------------------------------------------------------------------------------

\end{document}
